Finch: A Datastructure-Driven Array Programming Language

### 2024-03-20 sections/eval.tex
Update on Overleaf.

\subsubsection{Tensor Formats}
We benchmarked the SpMV kernel using the Dense level format for the outer level and the SparseList, SparseVBL, SparseBand, and SparsePoint Finch levels for the inner level of the sparse matrix. To represent scalar values, we benchmarked with both the Element and Pattern levels. The SparseList, SparseVBL, and SparseBand formats were functional for all matrices, but the SparsePoint format was applicable only for the synthetic permutation matrices. The Element format was applicable to represent scalars in all matrices, while the Pattern level was applicable only for boolean matrices. We tested with both the row-major and the column-major implementations (labeled with a "R" and "C", respectively, where applicable in Figure \ref{spmv_grouped}

>>>>

\subsubsection{Tensor Formats}
We benchmarked the SpMV kernel using the Dense level format for the outer level and the SparseList, SparseVBL, SparseBand, and SparsePoint Finch levels for the inner level of the sparse matrix. To represent scalar values, we benchmarked with both the Element and Pattern levels. The SparseList, SparseVBL, and SparseBand formats were functional for all matrices, but the SparsePoint format was applicable only for the synthetic permutation matrices. The Element format was applicable to represent scalars in all matrices, while the Pattern level was applicable only for boolean matrices. We tested with both the row-major and the column-major implementations (labeled with a "R" and "C", respectively, where applicable in Figure \ref{spmv_grouped}) with Finch.
